\SuperScreen: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2022-04-15 main.tex
bump superscreen version to 0.5.0
update tex

In this section we give a high-level overview of the \SuperScreen package. Further details can be found in the online documentation~\cite{superscreen-rtd}. The specific version of the package corresponding to this manuscript is \texttt{v0.4.0}.

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{examples/images/squid-mutuals.pdf}
    \caption{Calculating SQUID susceptometer mutual inductance, defined as the fluxoid induced in the SQUID pickup loop per unit current flowing in the field coil: $M_\mathrm{PL-FC}=\Phi^f_\mathrm{PL} / I_\mathrm{FC}$. Top row ({\bf a}): Schematics of \SuperScreen models for the field coil and pickup loop region of four sizes of scanning SQUID susceptometer (generated using \inline{Device.draw()}) with pickup loop inner radii ranging from $0.1\,\um$ (``Small'') to $3\,\um$ (``X-Large''). Middle row ({\bf b}): Simulated magnetic field $\mu_0H_z$ evaluated at the plane of layer W1, which contains the pickup loop, normalized by the current $I_\mathrm{FC}$ flowing in the field coil (which is located in layer BE). Bottom row ({\bf c}): Convergence of the four models, defined as the fractional change in mutual inductance between subsequent iterations $i$. For all four models, the simulated mutual inductance, $M_\mathrm{sim}$, falls within the range of mutual inductance values measured in real devices, $M_\mathrm{exp}$, which were reported in Table 1 of Ref.~\cite{Kirtley2016-zz}. The mutual inductance values are shown in units of $\Phi_0 / \mathrm{A}$, where $1\,\Phi_0 / \mathrm{A}\approx2.068\times10^{-3}\,\mathrm{pH}$. The meshes for the ``Small,'' ``Medium,'' and ``Large'' models consisted of approximately 7,000 vertices and 14,000 triangles, whereas the mesh for the ``X-Large'' model consisted of about 8,000 vertices and 15,000 triangles. The two smaller models converge more quickly than the two larger models for reasons discussed in \ref{appendix:numerics}. Note that for the ``X-Large'' model, we set the thicknesses of layers I1 and I2 both to 400 nm (instead of the nominal values of 150 nm and 130 nm respectively), to ensure convergence (see \ref{appendix:numerics} and Figure~\ref{fig:xlarge-dz-dr}).}
    \label{fig:squid-mutuals}
\end{figure*}

@@

Note that, unlike Equation~\ref{eq:london} in which $\Lambda$ is assumed to be constant as a function of position $\pvec{r}$, solutions to Equation~\ref{eq:london_inhomogeneous_2d} do not necessarily satisfy the fluxoid quantization condition $\Phi^f_S=0$ for simply-connected superconducting regions $S$ in which $\vec{\nabla}\Lambda(\pvec{r})\neq0$ , where
\begin{equation}
	\Phi^f_S=\underbrace{\int_S\mu_0H_z(\pvec{r})\,\mathrm{d}^2r}_{\text{``flux part''}} + \underbrace{\oint_S\mu_0\Lambda(\pvec{r})\vec{J}(\pvec{r})\cdot\mathrm{d}\pvec{r}}_{\text{``supercurrent part''}}.
\end{equation}
%As a (somewhat contrived) example, Code Block~\ref{code:inhomogeneous} demonstrates how to modify the model of a ring with a slit from Code Block~\ref{code:device} and Figure~\ref{fig:ring-with-slit} such that the ring's penetration depth $\Lambda(x, y)$ increases linearly as a function of the angle between the vector $\vec{r} = (x, y)$ and the $-y$ axis (along which the slit lies). The resulting current and field distributions, and the deviation from perfect fluxoid quantization, are shown in Figure~\ref{fig:inhomogeneous}.
%Note that $\Lambda(x, y)$ must vary slowly on the scale of the spacing between mesh vertices in order for results to be reliable. For example, the simulated supercurrent density near a point-like defect (i.e small compared to the triangles in the mesh) associated with a penetration depth $\Lambda_\text{defect}$ in an otherwise uniform film with penetration depth $\Lambda_0\ll\Lambda_\text{defect}$ will depend strongly on the specifics of the mesh near the defect. One can avoid this problem by increasing the density of the mesh in regions of fast-varying $\Lambda$ by adding one or more ``abstract regions" to the \inline{Device} as described in Section~\ref{section:overview:device}.

% \begin{code}
% \begin{minted}[fontsize=\small]{python}
% def linear_vs_angle(
%     x: np.ndarray, y: np.ndarray, *, min_val: float, max_val: float
% ) -> np.ndarray:
%     # Rotate the input coordinates so that theta = 0
%     # corresponds to the slit position (along the -y axis).
%     x, y = sc.geometry.rotate(
%         np.stack(np.atleast_1d(x, y), axis=1), np.degrees(-np.pi / 2)
%     ).T
%     # Calculate the angular position of each mesh vertex.
%     angles = np.arctan2(y, x) + np.pi  # range: [0, 2 * pi]
%     # Set Lambda to increase linearly from min_val to max_val
%     # as a function of angular position.
%     Lambdas = angles / (2 * np.pi) * (max_val- min_val) + min_val
%     return Lambdas
%
% # Define the Parameter and assign it as the Lambda of the superconducting layer.
% Lambda = sc.Parameter(linear_vs_angle, min_val=0.1, max_val=1.0)
% device.layers["base"].Lambda = Lambda
% # Everything below is identical to Code Block 1:
% # Calculate the device's response to a uniform applied field.
% applied_field = sc.sources.ConstantField(1)
% solution = sc.solve(device, applied_field=applied_field, field_units="mT")[-1]
% # Visualize the solution.
% # Plot the current density evaluated at each layer in the Device.
% solution.plot_currents()
% # Plot the magnetic field evaluated at each layer in the Device.
% solution.plot_fields()
% # Plot the field evaluated at any points in space.
% solution.plot_field_at_positions(device.points, zs=0.5)
% \end{minted}
% \captionof{listing}{Simulating an inhomogeneous superconducting device. Here we modify the superconducting ring with a slit from Code Block~\ref{code:device} and Figure~\ref{fig:ring-with-slit} to have an effective penetration depth $\Lambda(x, y)$, which increases linearly from $0.1\,\um$ to $1\,\um$ as a function of the angle between the vector $\vec{r}=(x, y)$ and the $-y$ axis. See Figure~\ref{fig:inhomogeneous} for the resulting current and field distributions.}
% \label{code:inhomogeneous}
% \end{code}
% \begin{figure*}[h!]
%     \centering
%     \includegraphics[width=\textwidth]{examples/images/ring_with_slit_inhomogeneous.pdf}
%     \caption{The output of Code Block~\ref{code:inhomogeneous}: Meissner screening of a uniform applied field of $1\,\mathrm{mT}$ by a ring with a slit in a superconducting film with inhomogeneous effective penetration depth $\Lambda(x, y)$. ({\bf a}) The inhomogeneous effective penetration depth $\Lambda(x, y)$, with the ring's outline overlaid in pink. Dashed squares indicate regions $S$ for which we calculate the fluxoid $\Phi^f_S$ in panel ({\bf e}). ({\bf b}) The current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}. ({\bf c}) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}. ({\bf d}) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}). ({\bf e}) The fluxoid $\Phi^f_S$ for each of the six square fluxoid regions, $S$, shown with dotted lines in ({\bf a}). Unlike Equation~\ref{eq:london} (where $\Lambda$ is constant as a function of position), solutions to Equation~\ref{eq:london_inhomogeneous_2d} do not necessarily satisfy fluxoid quantization, $\Phi^f_S=0$ for simply-connected superconducting regions $S$. $\Delta=\Phi^f_S / \int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r$ is the deviation from perfect quantization, i.e. the total fluxoid expressed as a percentage of the flux part. In general we expect $\Delta$ to be largest in regions $S$ in which the gradient of the effective penetration depth $\vec{\nabla}\Lambda$ is large.}
%     \label{fig:inhomogeneous}
% \end{figure*}

% As mentioned in Section~\ref{section:overview:device}, the effective penetration depth $\Lambda$ of each layer can be specified as a numeric constant or as a \inline{superscreen.Parameter} that computes $\Lambda(x, y)$, the effective penetration depth as a function of position. As a (somewhat contrived) example, Code Block~\ref{code:inhomogeneous} demonstrates how to modify the model of a ring with a slit from Code Block~\ref{code:device} and Figure~\ref{fig:ring-with-slit} such that the ring's penetration depth $\Lambda(x, y)$ increases linearly as a function of the angle between the vector $\vec{r} = (x, y)$ and the $-y$ axis (along which the slit lies). The resulting current and field distributions are shown in Figure~\ref{fig:inhomogeneous}. Note that $\Lambda(x, y)$ must vary slowly on the scale of the spacing between mesh vertices in order for results to be reliable. For example, the simulated supercurrent density near a point-like defect (i.e small compared to the triangles in the mesh) associated with a penetration depth $\Lambda_\text{defect}$ in an otherwise uniform film with penetration depth $\Lambda_0\ll\Lambda_\text{defect}$ will depend strongly on the specifics of the mesh near the defect. One can avoid this problem by increasing the density of the mesh in regions of fast-varying $\Lambda$ by adding one or more ``abstract regions" to the \inline{Device} as described in Section~\ref{section:overview:device}.

>>>>

In this section we give a high-level overview of the \SuperScreen package. Further details can be found in the online documentation~\cite{superscreen-rtd}. The specific version of the package corresponding to this manuscript is \texttt{v0.5.0}.

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{examples/images/squid-mutuals.pdf}
    \caption{Calculating SQUID susceptometer mutual inductance, defined as the fluxoid induced in the SQUID pickup loop per unit current flowing in the field coil: $M_\mathrm{PL-FC}=\Phi^f_\mathrm{PL} / I_\mathrm{FC}$. Top row ({\bf a}): Schematics of \SuperScreen models for the field coil and pickup loop region of four sizes of scanning SQUID susceptometer (generated using \inline{Device.draw()}) with pickup loop inner radii ranging from $0.1\,\um$ (``Small'') to $3\,\um$ (``X-Large''). Middle row ({\bf b}): Simulated magnetic field $\mu_0H_z$ evaluated at the plane of layer W1, which contains the pickup loop, normalized by the current $I_\mathrm{FC}$ flowing in the field coil (which is located in layer BE). Bottom row ({\bf c}): Convergence of the four models, defined as the fractional change in mutual inductance between subsequent iterations $i$. For all four models, the simulated mutual inductance, $M_\mathrm{sim}$, falls within the range of mutual inductance values measured in real devices, $M_\mathrm{exp}$, which were reported in Table 1 of Ref.~\cite{Kirtley2016-zz}. The mutual inductance values are shown in units of $\Phi_0 / \mathrm{A}$, where $1\,\Phi_0 / \mathrm{A}\approx2.068\times10^{-3}\,\mathrm{pH}$. The meshes for all four models consisted of approximately 6,000 vertices and 12,000 triangles. The two smaller models converge more quickly than the two larger models for reasons discussed in \ref{appendix:numerics}. Note that for the ``X-Large'' model, we set the thicknesses of layers I1 and I2 both to 400 nm (instead of the nominal values of 150 nm and 130 nm respectively), to ensure convergence (see \ref{appendix:numerics} and Figure~\ref{fig:xlarge-dz-dr}).}
    \label{fig:squid-mutuals}
\end{figure*}

@@

Note that, unlike Equation~\ref{eq:london} in which $\Lambda$ is assumed to be constant as a function of position $\pvec{r}$, solutions to Equation~\ref{eq:london_inhomogeneous_2d} do not necessarily satisfy the fluxoid quantization condition $\Phi^f_S=0$ for simply-connected superconducting regions $S$ in which $\vec{\nabla}\Lambda(\pvec{r})\neq0$ , where
\begin{equation}
	\Phi^f_S=\underbrace{\int_S\mu_0H_z(\pvec{r})\,\mathrm{d}^2r}_{\text{``flux part''}} + \underbrace{\oint_S\mu_0\Lambda(\pvec{r})\vec{J}(\pvec{r})\cdot\mathrm{d}\pvec{r}}_{\text{``supercurrent part''}}.
\end{equation}
